False Discovery Rates, A New Deal

### 2015-03-16 Rcode/efron.fcr.rmd
some updates to fcr and paper

```{r}
  set.seed(100)
  nsamp=10000
  mu0 = rep(0,nsamp)
  mu1 = rnorm(nsamp,-3,1)
  comp = rbinom(nsamp,1,0.1)
  mu = ifelse(comp==0,mu0,mu1)
  z = rnorm(nsamp,mu,1)
```

```{r}
  library(ashr)
  res.ash = ash(z,1,mixcompdist="halfuniform",method="fdr")
  CImatrix= ashci(res.ash,level=0.95)
```

Compare results with Bayes rule
```{r}
  BayesComparePlot=function(){
    plot(z,mu,xlim=c(-8,0))
    points(z[CImatrix[,1]],CImatrix[,5],col="red")
    points(z[CImatrix[,1]],CImatrix[,4],col="red")

    fdr = 0.9*dnorm(z)/(0.9*dnorm(z)+0.1*dnorm(z,-3,sqrt(2)))
    o=order(z)
    upper = ifelse(fdr[o]<0.025,(z[o]-3)/2+qnorm(0.975+fdr[o])/sqrt(2),0)
    lines(z[o],upper,col="green",lwd=2)
    lines(z[o],(z[o]-3)/2-qnorm(0.975)/sqrt(2),col="green",lwd=2)
    abline(v=max(z[fdr<0.05]))
  }
  BayesComparePlot()
```

@@

```{r}
   res.ash = ash(z,1,mixcompdist="halfuniform",method="fdr")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

@@

```{r}
   res.ash = ash(z,1,mixcompdist="normal",method="fdr")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

And uniform mixture:
```{r}
   res.ash = ash(z,1,mixcompdist="uniform",method="fdr")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

>>>>

```{r}
  set.seed(100)
  nsamp=10000
  altmean=-3
  mu0 = rep(0,nsamp)
  mu1 = rnorm(nsamp,altmean,1)
  comp = rbinom(nsamp,1,0.1)
  mu = ifelse(comp==0,mu0,mu1)
  z = rnorm(nsamp,mu,1)
```

```{r}
  library(ashr)
  res.ash = ash(z,1,mixcompdist="halfuniform")
  CImatrix= ashci(res.ash,level=0.95)
```

Compare results with Bayes rule
```{r}
  BayesComparePlot=function(altmean=-3){
    plot(z,mu,xlim=c(-8,0))
    points(z[CImatrix[,1]],CImatrix[,5],col="red")
    points(z[CImatrix[,1]],CImatrix[,4],col="red")

    fdr = 0.9*dnorm(z)/(0.9*dnorm(z)+0.1*dnorm(z,altmean,sqrt(2)))
    o=order(z)
    upper = ifelse(fdr[o]<0.025,(z[o]+altmean)/2+qnorm(0.975+fdr[o])/sqrt(2),0)
    lines(z[o],upper,col="green",lwd=2)
    lines(z[o],(z[o]+altmean)/2-qnorm(0.975)/sqrt(2),col="green",lwd=2)
    abline(v=max(z[fdr<0.05]))
  }
  BayesComparePlot(altmean)
```

@@

```{r}
   res.ash = ash(z,1,mixcompdist="halfuniform")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

@@

```{r}
   res.ash = ash(z,1,mixcompdist="normal")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

And uniform mixture:
```{r}
   res.ash = ash(z,1,mixcompdist="uniform")
  CImatrix= ashci(res.ash,level=0.95)
  BayesComparePlot()
```

### 2015-03-16 paper/main.tex
split ash into ash and ash.workhorse
updated dsc-shrink
some updates to fcr and paper

Show that the q values are driven by changes in pi_0; even when not unimodal pretty close...

@@

@@

>>>>

Show that the q values are driven by changes in $\pi_0$; even when not unimodal pretty close...

@@

\subsubsection*{Reverse asymptotics}

@@

\subsection*{False Coverage Rates}

To summarize the False Coverage Rate problem, we can do no better than quote Efron, who says
``An insightful and ingenious paper by Benjamini and
Yekutieli (2005) discusses the following problem in simultaneous
significance testing: having applied false
discovery rate methods to select a set of nonnull cases,
how can confidence intervals be assigned to the true
effect size for each selected case?" \cite{efron2008} notes the potential for EB approaches to tackle this problem,
but also notes the difficulties of implementing a stable general algorithm.
%deconvolution
%calculations are notoriously tricky and I have not
%been able to produce a stable general algorithm. ; see also 
Zhao+Hwang consider in detail the case where the non-null effects are normally distributed.

Results in efron.fcr.rmd suggests that lower CI is OK; upper is more problematic because of difficulty in accurately estimating tail?

To do: implement methods to compute posterior cdf of each observation at given points. 
Then compute these for the simulation studies. Check whether issue with upper bound is due to non-unimodal distribution.

### 2015-03-16 talks/one_hour_seminar.Rmd
some updates to fcr and paper

---
title: "False Discovery Rates, A New Deal"
author: Matthew Stephens
date: February 3, 2015
output: ioslides_presentation
---

@@

- `ashr` package: `http://www.github.com/stephens999/ash`

>>>>

---
title: "False Discovery Rates, A New Deal"
author: Matthew Stephens
date: March 9, 2015
output: ioslides_presentation
---

@@

- `ashr` package: `http://www.github.com/stephens999/ashr`
